Probabilistic Catalogs from Crowded Star Fields

### 2012-07-27 paper/ms.tex
CDFs
Got the PDF - much nicer

\section{Broken Pareto Distribution}
The Broken Pareto distribution is:
\begin{eqnarray}
p(x | \theta) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
We will need the fully normalised version. Putting in two normalising constants:
\begin{eqnarray}
p(x | \theta) &=&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
C_1x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
C_2x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
The normalising constants can be obtained by enforcing the following
constraints. The first constraint is that the total probability is unity:
\begin{eqnarray}
\int p(x|\theta) \, dx = 1
\end{eqnarray}
The second constraint is that the PDF should be continuous at $x=x_1$:
\begin{eqnarray}
C_1 x_1^{-\alpha_1 - 1} = C_2 x_1^{-\alpha_2 - 1}
\end{eqnarray}

>>>>

\section{Broken Pareto Distribution}

Consider the complementary CDF:
\begin{eqnarray}
G(x) = P(X \geq x)
\end{eqnarray}
The complementary CDF for a broken Pareto is:
\begin{eqnarray}
G(x) &=&
\left\{
\begin{array}{lcr}
1, & & x < x_1 \\
\left(\frac{x_1}{x}\right)^{\alpha_1}, & & x_1 \leq x \leq x_2 \\
K\left(\frac{x_2}{x}\right)^{\alpha_2}, & & x > x_2
\end{array}
\right.
\end{eqnarray}
Since we want the CDF to be continuous (to avoid delta functions in the PDF!)
then the value of $K$ must be set by:
\begin{eqnarray}
\left(\frac{x_1}{x_2}\right)^{\alpha_1} &=& K\left(\frac{x_2}{x_2}\right)^{\alpha_2} \\
\implies K &=& \left(\frac{x_1}{x_2}\right)^{\alpha_1}.
\end{eqnarray}
Therefore the complementary CDF is:
\begin{eqnarray}
G(x) &=&
\left\{
\begin{array}{lcr}
1, & & x < x_1 \\
\left(\frac{x_1}{x}\right)^{\alpha_1}, & & x_1 \leq x \leq x_2 \\
\left(\frac{x_1}{x_2}\right)^{\alpha_1}\left(\frac{x_2}{x}\right)^{\alpha_2}, & & x > x_2
\end{array}
\right.
\end{eqnarray}
From this we can obtain the standard CDF:
\begin{eqnarray}
F(x) &=& P(X \leq x) \\
&=& 1 - G(x)\\
&=& \left\{
\begin{array}{lcr}
0, & & x < x_1 \\
1 - \left(\frac{x_1}{x}\right)^{\alpha_1}, & & x_1 \leq x \leq x_2 \\
1 - \left(\frac{x_1}{x_2}\right)^{\alpha_1}\left(\frac{x_2}{x}\right)^{\alpha_2}, & & x > x_2
\end{array}
\right.
\end{eqnarray}
The probability density function (PDF) can be obtained by differentiation:
\begin{eqnarray}
f(x) &=& \frac{d}{dx} F(x) \\
&=& \left\{
\begin{array}{lcr}
0, & & x < x_1 \\
\left[\alpha_1 x_1^{\alpha_1}\right]x^{-\alpha_1 - 1}, & & x_1 \leq x \leq x_2 \\
\left[\alpha_2 x_1^{\alpha_1} x^{\alpha_2 - \alpha_1}\right]x^{-\alpha_2 - 1}, & & x > x_2
\end{array}
\right.
\end{eqnarray}
The normalization constants are the factors inside square brackets.
